ODGI: scalable tools for pangenome graphs

### 2021-07-11 manuscript/main.tex
typos

    Thanks to advances in sequencing technology, new full-length
    genome assemblies are produced at a high rate, including efforts
    from the Human Pangenome Reference Consortium (HPRC) and
    telomere-to-telemere projects, e.g.~\citep{Miga:2020}. In
    principle, a pangenome can model a full set of genomic elements of
    individuals in a given species or clade. Pangenomics contrasts
    with reference genome based approaches which relate sequences to a
    single consensus model of the genome~\citep{Eizenga:2020}. A
    pangenome can elegantly be represented by a graph data structure
    incorporating sequences as nodes and their connections as
    edges. These nodes are shared for identical sequences, such as
    homologs, paralogs and orthologs. So-called paths can represent
    reads, contigs, haplotypes, individual chromosomes or part
    thereof, that run through the nodes. A bi-directed graph can even
    contain both strands of DNA as paths. A graph-based approach is
    particularly relevant for exploring complex variation and highly
    repetitive regions, such as the Major Histocompatibility Complex
    (MHC, Fig.~\ref{fig:1}).

>>>>

    Thanks to advances in sequencing technology, new full-length
    genome assemblies are produced at a high rate, including efforts
    from the Human Pangenome Reference Consortium (HPRC) and
    telomere-to-telomere projects, e.g.~\citep{Miga:2020}. In
    principle, a pangenome can model a full set of genomic elements of
    individuals in a given species or clade. Pangenomics contrasts
    with reference genome based approaches which relate sequences to a
    single consensus model of the genome~\citep{Eizenga:2020}. A
    pangenome can elegantly be represented by a graph data structure
    incorporating sequences as nodes and their connections as
    edges. These nodes are shared for identical sequences, such as
    homologs, paralogs and orthologs. So-called paths can represent
    reads, contigs, haplotypes, individual chromosomes or part
    thereof, that run through the nodes. A bi-directed graph can even
    contain both strands of DNA as paths. A graph-based approach is
    particularly relevant for exploring complex variation and highly
    repetitive regions, such as the Major Histocompatibility Complex
    (MHC, Fig.~\ref{fig:1}).
